### 2013-09-14 research/paper/introduction/intro-1.0.tex
uploaded 7.45

According to \cite{Paidoussis2010},\cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.  \cite{DenHartog1956}  has provided a theoretical explanation for galloping for iced electric transmission lines. A non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory. Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model. It essentially used a curve fit of the transverse force to predict the galloping response. The study managed to achieve a good agreement with experimental data. The QSS model equation when solved using analytically using sinusoidal solution mehod cannot predict cases with low mass ratios  .\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio. The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.
\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory. In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio
 the mass-damping ($m^*\zeta$) parameter should be kept low as well as the frequency of oscillations should be carefully matched with the size of the cross section. Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.

>>>>

According to \cite{Paidoussis2010},\cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.  \cite{DenHartog1956}  has provided a theoretical explanation for galloping for iced electric transmission lines. A non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory. Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model. It essentially used a curve fit of the transverse force to predict the galloping response. The study managed to achieve a good agreement with experimental data. The QSS model equation when solved using analytically using sinusoidal solution method cannot predict cases with low mass ratios  .\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio. The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.
\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory. In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low. Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.

### 2013-09-14 research/paper/results/results-2.3.tex
uploaded 7.45

>>>>

In this paper, the power transfer of a square body under aero elastic galloping is analysed by using quasi-steady state model and numerical methods. The system is not frequency dependent but more dependent on the velocity amplitude of they system. It could be proven from the collapsed plots in terms of non-dimensionalised (using flow parameters) damping constant. By anaylizing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($c\rho\mathcal{A}U$) should be high, but not too high enough to hinder the induced angle of attack reaching the region of higher forcing. The reduction in power at low mass ratios was due to the fact that the instantaneous $P_t$ and $P_d$ are not the same. Therefore the mechanical system requires adequate inertia to store a portion of power transferred from the fluid to the body to sustain galloping.
